Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-07-12 paper.tex
Add some notes on Homogeneous Equilibrium test

\subsection{Infinite Homogeneous Slab:
  Testing Thermodynamic Equilibrium}
\label{ssec:test_equilibrium}
In an optically thick region the radiation field is in thermodynamic equilibrium
with the matter.
We set up a large slab of matter in two homogeneous configurations
representative of the fluid in the Massive Collapsed Star test
(Sec.~\ref{ssec:test_collapse}) at the radius 50~km.
For comparision with Collapsed Star test, we use the LS180 equation of state,
in which the equilibrium $\nu_e$ neutrino chemical potential is
$\mu_{\nu_e}=-0.575$~MeV
($\mu_{\bar{\nu}_e}=-\mu_{\nu_e}$ and $\mu_{\nu_x}=0$).
Plot in Fig.~\ref{fig:homogeneous_isotropic}.
\todo{also describe this test with scat}

>>>>

\subsection{Infinite Homogeneous Slab:
  Testing Thermodynamic Equilibrium}
\label{ssec:test_equilibrium}
In an optically thick region the radiation field is in thermodynamic equilibrium
with the matter.
We set up a large slab of matter
representative of the fluid in the Massive Collapsed Star test
(Sec.~\ref{ssec:test_collapse}) at the radius 50~km.
For comparision with that test we use the LS180 equation of state
\cite{latt1991-nuc_eos}
\footnote{available at \lstinline{stellarcollapse.org}}
in which the equilibrium $\nu_e$ neutrino chemical potential is
$\mu_{\nu_e}=-0.575$~MeV
(with $\mu_{\bar{\nu}_e}=-\mu_{\nu_e}$ and $\mu_{\nu_x}=0$).
Fig.~\ref{fig:mfps-50km} presents the neutrino mean free paths
at this thermodynamic point over two energy decades.
For this test we set up our slab large enough for neutrinos of all
energies to be trapped. 
Since our ray tracing algorithm integrates rays to terminal optical
depths of $\tau_{\rm term}>14$, our domain must extend to $r=10^7\,{\rm km}$.

Fig.~\ref{fig:cumulative_f_homogeneous} displays the integrated $f$ as a
function of path length along the ray.

Fig.~\ref{fig:homogeneous_isotropic} shows the error in our results.
\todo{describe with scat on}
